% -------------------------
% Resume in Latex
% ------------------------

\documentclass[letterpaper, 10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage[document]{ragged2e}

\listfiles

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\setlength{\footskip}{4.35004pt}

\urlstyle{same}

\raggedbottom{}
\raggedright{}
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule{} \vspace{-5pt}]

% Custom commands
\newcommand{\resumeItem}[2]{
\item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
  \newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\justify\begin{itemize}}
  \newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% -------------------------------------------
%%%%%% CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

% ----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Thomson Knoles} & Email: \href{mailto:thomsonknoles@gmail.com}{thomsonknoles@gmail.com}\\
  Asheville, NC & Phone: +1 (928) 853-7104 \\
\end{tabular*}

% -----------SUMMARY-----------------
\section{Summary}
Australian-born jazz pianist, producer, and beat-maker with over a decade of experience in live performance, composition, and music production. Specializes in blending traditional jazz with modern sounds. Notable achievements include producing music for Nike's 2022 Fathers Day commercial and extensive touring experience across the U.S. and international jazz festivals.

% -----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Freelance Music Producer}{Asheville, NC}
{Music Producer and Composer}{2020 -- Present}
\resumeItemListStart
\resumeItem{Produced music for Nike’s Fathers Day commercial}{Collaborated with various artists, focusing on jazz fusion and electronic music.}
\resumeItemListEnd
\vspace{15pt}
\resumeSubheading
{The Fritz}{Asheville, NC}
{Pianist}{2018 -- Present}
\resumeItemListStart
\resumeItem{Key member of the Asheville-based band}{Contributed to live performances and recording sessions, combining jazz, funk, and electronic elements.}
\resumeItemListEnd
\vspace{15pt}
\resumeSubheading
{Felix Pastorius Trio}{Asheville, NC}
{Pianist}{2022 -- Present}
\resumeItemListStart
\resumeItem{One-third of the trio}{Performed at high-profile jazz venues, blending improvisation and technical mastery.}
\resumeItemListEnd
\vspace{15pt}
\resumeSubheading
{STIG (Instrumental Funk Fusion Band)}{U.S. (26 states)}
{Founder and Touring Musician}{2016 -- 2020}
\resumeItemListStart
\resumeItem{Founded and led the funk fusion band STIG}{Toured extensively across the U.S., performing at diverse venues, from dive bars to sold-out theaters.}
\resumeItemListEnd
\vspace{15pt}
\resumeSubheading
{Copenhagen Jazz Festival}{Copenhagen, Denmark}
{Jazz Pianist}{2014, 2015}
\resumeItemListStart
\resumeItem{Performed at the prestigious Copenhagen Jazz Festival}{Showcased original compositions and jazz standards.}
\resumeItemListEnd
\vspace{15pt}
\resumeSubHeadingListEnd

% -----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart

\resumeSubheading
{Berklee College of Music}{Boston, MA}
{Bachelor of Music in Jazz Performance}{2016}
\resumeItemListStart
\resumeItem{Received the prestigious Jazz Performance Award}{2015.}
\resumeItemListEnd
\vspace{15pt}
\resumeSubheading
{Flagstaff Arts and Leadership Academy}{Flagstaff, AZ}
{High School Diploma}{2010}
\resumeSubHeadingListEnd

% -----------KEY SKILLS-----------------
\section{Key Skills}
\resumeSubHeadingListStart
\resumeItem{Performance}{Jazz Piano, Composition, Improvisation, Beat-Making}
\resumeItem{Production}{Music Production, Sound Engineering, DAW Proficiency}
\resumeItem{Touring}{Live Performances, Band Leadership, Touring Experience}
\resumeSubHeadingListEnd

% -----------NOTABLE ACHIEVEMENTS-----------------
\section{Notable Achievements}
\resumeSubHeadingListStart
\resumeItem{Produced Music for Nike's Fathers Day Commercial}{2022}
\resumeItem{Jazz Performance Award Recipient}{Berklee College of Music, 2015}
\resumeItem{Touring with STIG}{Performed across 26 U.S. states, 2016–2020}
\resumeItem{Copenhagen Jazz Festival Performer}{2014, 2015}
\resumeSubHeadingListEnd

% ------------REFERENCES-----------------
\section{References}
Available upon request.

% -------------------------------------------
\end{document}
